Mathematical Formulation of Projection Problem

### 2024-09-04 docs/logbook.tex
Updates to logbook and projection

>>>>

	\begin{MeetingMinutes}{Sun 18/08/2024}{u7013004}
		Going to work on optimising the volume to be a certain target now and read a paper. Then, I'll write some things in the template. Efficiency!
	\end{MeetingMinutes}

	\begin{MeetingMinutes}{Wed 4/09/2024}{u7013004}
		For the past few days, I've been trying to mathematically formulate the projection. Just tested it in code today and it seems that I am minimising the area of the cross-section with the $x$-$y$ plane instead. So, just need to take Schur complement instead of projection with matrix P.
	\end{MeetingMinutes}
